Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-17 paper/sections/abstract.tex
[ paper ] abstract reviewed.

\begin{abstract}
In this paper, we describe our approach to reconstruct and verify in
\Agda proof assistant, solutions generated by \Metis prover to problems in classical propositional logic. The translation method consists of justifying
step-by-step each deduction found in the prover's solution. To carry
out this plan, we emulate the inference rules of the prover,
providing a version of them in the proof assistant. Finally, we
parse the output of the prover, build and analyze the respective
tree associated with the proof, for ending up with an \Agda code of
the proof for type-checking.

\keywords{proof-reconstruction, \Agda, automatic theorem prover,
classical propositional logic, \Metis.}

>>>>

\begin{abstract}
In this paper, we describe a syntactical proof-reconstruction
approach to verify solutions generated by \Metis prover to problems in classical propositional logic without equality.
To verify these \Metis derivations, we translate them automatically
to \Agda proof-terms.
Using the proof-assistant, we were able to type-check the
formalization approach presented in this work. A formulation about
the inference rules used by \Metis.
This allowed us to type-check proof-objects step-by-step.

\keywords{proof-reconstruction, type theory, \Agda, automatic
theorem prover, classical propositional logic, \Metis.}
